Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-21 edubots_surveys.Rnw
Adds suggestion by @noorhanabbas

% Olia: we have something for RQ 2 and 4.
 One of the most interesting questions that can arise from the plots, and the should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom? The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed. Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.

% Noorhan comments negative experience with customer service chatbots, in which case people will not see the value of using it in their classes. They are not aware of something like that. Teaching chatbots are difficult to develop. Using very simple chatbots, or simply conversational interfaces, could help introduce this technology - JJ

>>>>

 One of the most interesting questions that can arise from the analysis of the results, and that should require further study, is: Are teachers really aware of the possibilities of chatbots in the classroom? The reason to ask ourselves this question is due to the fact of the small number of responses for other uses in comparison with the other approaches proposed. Another way to look about it is that, unless you provide the specific instructions on how to use a tool, the teaching staff is already too busy or burn out to think about innovation.

It is also likely that their opinions towards chatbots are informed by negative experiences with customer support chatbots, which is what most people will have experienced. This will probably require further study, but also will need to be taken into account when introducing chatbot technologies in the classroom: it will have to be as simple, and as satisfactory, ad possible, to (possibly) delete this existing perception.
